---
title: "Non-Standard Families of Tests"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(wildrwolf)
```

At the moment, the `rwolf()` function does not support many different types of families of tests. E.g. if you had estimated the following two regression models 

$$
   Y = \beta_0 + \beta_1 X_1 + \beta_2 X2 + u
$$
and 

$$
   Y = \beta_0 + \beta_3 X_3 + u
$$
and wanted to correct the following family of hypotheses for multiple testing: 

$$
H_{0,A}: \beta_1 = 0 \text{ vs } H_{1,A}: \beta_1 \neq 0
$$
$$
H_{0,B}: \beta_2 = 0 \text{ vs } H_{1,B}: \beta_2 \neq 0
$$

$$
H_{0,C}: \beta_1 + \beta_2 = 0 \text{ vs } H_{1,C}: \beta_1 + \beta_2\neq 0
$$ 
$$
H_{0,D}: \beta_3 = 0 \text{ vs } H_{1,D}: \beta_3 \neq 0.
$$

Unfortunately, the current API of `rwolf()` does not yet support such a family of tests. To apply the Romano Wolf corrections for this family, you would have to follow three steps outlined below. But first, let's simulate some data. 

```{r}
N <- 1000
X1 <- rnorm(N) 
X2 <- rnorm(N) 
X3 <- rnorm(N)
Y <- 1 + 0.001 * X1 + 0.001 * X2 + 0.5 *X3 + rnorm(N)
cluster <- sample(1:20, N, TRUE)
df <- data.frame(Y = Y, X1 = X1, X2 = X2, X3 = X3, cluster)
```

### Step 1: Estimate two regression models via `fixest`

```{r}
library(fixest)

fit1 <- feols(Y ~ X1 + X2, data = df, cluster = ~cluster)
fit2 <- feols(Y ~ X3, data = df, cluster = ~cluster)
```

### Step 2: Create bootstrapped t-statistics via `fwildclusterboot::boottest()`. Make sure to reset the random seeds, so that all calls to `boottest()` use the same bootstrap weights

```{r}
library(fwildclusterboot)

set.seed(123)
boot1 <- boottest(fit1, param = ~X1, B = 9999, clustid = ~cluster)
set.seed(123)
boot2 <- boottest(fit1, param = ~X2, B = 9999, clustid = ~cluster)
set.seed(123)
boot3 <- boottest(fit1, param = ~X1 + X2, B = 9999, clustid = ~cluster)
set.seed(123)
boot4 <- boottest(fit2, param = ~ X3, B = 9999, clustid = ~cluster)

# get the bootstrapped t-stats from boottest
t_boot <- lapply(list(boot1, boot2, boot3, boot4), 
       function(x) x[["t_boot"]]) 
t_boot <- Reduce("cbind",t_boot)

# get the non-bootstrap t-stats from boottest
t_stat <-  lapply(list(boot1, boot2, boot3, boot4), 
       function(x) teststat(x)) 
t_stat <- Reduce("cbind",t_stat)

```

### Step 3: feed the bootstrapped and non-bootstrapped t-statistics into the `get_rwolf_pval()` function

```{r}
get_rwolf_pval(t_stats = t_stat, boot_t_stats = t_boot)
```

This returns a vector of multiple-testing adjusted pvalues for all hypotheses. 


